Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-26 paper/snakemajoranas.tex
small changes

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of Majorana wave functions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for the straight system is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for the zigzag systems.
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
\end{figure}

\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and a variant of the latter with disordered edges.
In figure~\ref{fig:wave_functions} the wave functions are displayed, superimposed upon their respective geometry.
By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
To determine $\xi_\textrm{M}$ for the zigzag systems, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum.
Using this system, we then find the Majorana size $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
This method is numerically not feasible for a straight system because the decay length is too long.
Instead, we find $\xi_\textrm{M}$ through the eigenvalue decomposition of the translation operator at zero energy as described in Ref.~\onlinecite{nijholt2015orbital}.
All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.

@@

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
We observe that for zigzag systems the Majorana properties improve independent of the details of the specific geometry.
All of the zigzag type geometries display a significantly reduced Majorana size which improves the localization of the Majorana wave functions as is visible in the density plots.
The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
Further, the topological gap is an order of magnitude higher, and as mentioned in section \ref{sec:band_structures}, the velocity is an order of magnitude lower.
Both of these parameters ensure that $\xi_\textrm{M}$ is greatly improved (Eq.~\eqref{eq:xi_M}).
Finally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

>>>>

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for the straight system is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for the zigzag systems.
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
\end{figure}

\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and a variant of the latter with disordered edges.
In figure~\ref{fig:wave_functions} the Majorana wave function densities $\left| \psi_\textrm{M} \right|^2$ are displayed, superimposed upon their respective geometry.
By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
To determine $\xi_\textrm{M}$ for the zigzag systems, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum.
Using this system, we then find the Majorana size $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
This method is numerically not feasible for a straight system because the decay length is too long.
Instead, we find $\xi_\textrm{M}$ through the eigenvalue decomposition of the translation operator at zero energy as described in Ref.~\onlinecite{nijholt2015orbital}.
All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.

@@

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
We observe that for zigzag systems the Majorana properties improve independent of the details of the specific geometry.
All of the zigzag type geometries display a significantly reduced Majorana size which improves the localization of the Majorana wave functions as is visible in the density plots.
The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher, and as mentioned in section \ref{sec:band_structures}, the velocity $v_\textrm{F}$ is an order of magnitude lower.
Both of these parameters ensure that $\xi_\textrm{M}$ is greatly improved (Eq.~\eqref{eq:xi_M}).
Finally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
